Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-25 paper/main.tex
minor copy edits to performance section

\begin{itemize}
    \item In standard tournaments the dominating strategies were
    strategies that had been trained using reinforcement learning techniques.
    \item In noisy environments where the noise probability strictly less than
    0.1 was considered, the successful strategies were strategies specifically
    designed or trained for noisy environments.
    \item In probabilistic ending tournaments most of the highly ranked
    strategies were defecting strategies and trained finite state automata, all
    by the authors of~\cite{Ashlock2006, Ashlock2014}. These strategies ranked
    high due to their performance in tournaments where the probability of the
    game ending after each turn was bigger than 0.1.
    \item In probabilistic tournaments with \(p_e\) less than 0.1 the highly
    ranked strategies were strategies based on the behaviour of others.
    \item From the collection of strategies considered here,  no strategy can be
    consistently successful in noisy environments, except if the value of noise
    is constrained to less than a 0.1.
\end{itemize}

Though there is not a single strategy that repeatably outranks all others in any
of the distinct tournament types, or even across the tournament types, there
are specific types of strategies have been repeatably ranked in the top ranks.
These have been strategies that have been trained, strategies that retailiate,
and strategies that would adapt their behaviour based on preassigned rules
to achieve the highest outcome. These results contradict some of R. Axelrod's suggestions,
and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
We dig deeper into the crucial strategy features for success in the following sections.

>>>>

\begin{itemize}
    \item In standard tournaments the dominating strategies were
    strategies that had been trained using reinforcement learning techniques.
    \item In noisy environments where a noise probability strictly less than
    0.1 was considered, the successful strategies were strategies specifically
    designed or trained for noisy environments.
    \item In probabilistic ending tournaments most of the highly ranked
    strategies were defecting strategies and trained finite state automata, all
    by the authors of~\cite{Ashlock2006, Ashlock2014}. These strategies ranked
    high due to their performance in tournaments where the probability of the
    game ending after each turn was bigger than 0.1.
    \item In probabilistic tournaments with \(p_e\) less than 0.1 the highly
    ranked strategies were strategies based on the behaviour of others.
    \item From the collection of strategies considered here,  no strategy can be
    consistently successful in noisy environments, except if the value of noise
    is constrained to less than a 0.1.
\end{itemize}

Though there is not a single strategy that repeatably outranks all others in any
of the distinct tournament types, or even across the tournament types, there
are specific types of strategies have been repeatably ranked in the top ranks.
These have been strategies that have been trained, strategies that retailiate,
and strategies that would adapt their behaviour based on preassigned rules
to achieve the highest outcome. These results contradict some of R. Axelrod's suggestions,
and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
We dig deeper into the crucial strategy features for success in the following section.
